Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-07 Dissertation/Thesis/tex/results.tex
updated from tlee edits, more figs for NRL flight experiment

The experiment involves a ground vehicle producing a probabilistic occupancy grid map in real time. The robot motion is governed by the information gain-maximizing policy described in Chapter \ref{chap:ae2D}.

% TL: add a figure of Pioneer
\subsection{Hardware Configuration}
The Pioneer 3 ground robot is chosen for this experiment because of its reliability and simple operation. The vehicle accepts two inputs, namely linear velocity (aligned with the robot wheels) and angular velocity (about a central axis passing vertically through the robot). The robot pose is estimated via Vicon Tracker, which provides the location and attitude of a rigid body. The depth readings are obtained by a Kinect depth sensor. Since the experiment is to map and explore a 2D environment, only a single central row of the 3D Kinect depth scan provide the necessary measurements. The robot captures an experimental environment with walls constructed from Styrofoam.

@@

% add citation for OpenGL
The software structure is similar to ROS nodes Section \ref{sec:Ae2DNumExamples}, which simply involves a mapping node, an exploration node, and a visualization node using OpenGL libraries. The only differences are eliminating the simulator (Stage) and adding synchronization among the sensors, which is of high importance to the proposed occupancy grid mapping approach. Any time delay between the robot pose estimation and the sensor depth readings can cause conflicting information, which may be harmful to the probabilistic map. Thus, ROS approximate message filters are applied such that the pose from Vicon Tracker ($100$Hz) and the Microsoft Kinect ($30$Hz) are nearly synchronized, which provides validity of the assumption that the measurement ray positions and directions are known deterministically.

\subsection{Exploring and Mapping a 2D Environment}
% TL: I wish there are more photos from the experiments 
The environment consists of Styrofoam walls on a flat floor. The perimeter is rectangular, with several obstacles and angled walls (see Figure \ref{fig:ExpSetupPhoto}). The robot autonomously explored the space using the complete Cartesian searching approach, and Dijkstra's algorithm provides collision-free waypoints to the optimal future poses. Based on these waypoints, a constrained least squares polynomial fitting generates a smooth trajectory to follow the waypoints with fixed velocity. Finally, a simple controller is implemented such that the Pioneer follows the trajectory by moving and orienting toward the desired robot location $1$ sec in the future.

@@

The quadrotor takes off, completes a rotation to understand its immediate surroundings, then explores the space over $2$ minutes and $47$ seconds. Figure \ref{fig:exp3DMap} shows the probabilistic 3D map generated in real-time at four selected times, and the corresponding 2D projected maps (x-direction upward) are illustrated in Figure \ref{fig:exp2DMap}, where arrows represent pose candidates and a trajectory is shown to the optimal pose. Figure \ref{fig:expH} shows the total map entropy decreasing over the experiment duration. A video of the experiment can be found at \href{https://www.youtube.com/watch?v=I_1rXV2XRqk}{\WriteBlue{https://www.youtube.com/watch?v=I\_1rXV2XRqk}}.

@@

% TL: add figures for more time instances
\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.65\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_0min.jpg}
        		\caption{$0$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.65\columnwidth}
		\vspace*{0.01\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.65\columnwidth}
	\vspace*{0.01\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.65\columnwidth}
	\vspace*{0.01\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_2min47sec.jpg}
        		\caption{$2$ min $47$ sec (end)}
    	\end{subfigure}
	\caption{3D Occupancy Grid Map During Level Flight Experiment}
	\medskip
	\small
	The 3D occupancy grid map is overlaid with point cloud measurements. The map probabilities directly rely on the Xtion and Hokuyo measurements and the sensor stochastic properties.
	\label{fig:exp3DMap}
\end{figure}

% TL: add figures for more time instances
\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_0min_2D.jpg}
        		\caption{$0$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_1min_2D.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_2min_2D.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_2min47sec_2D_labeled.jpeg}
        		\caption{$2$ min $47$ sec (end)}
    	\end{subfigure}
	\caption{2D Projected Occupancy Grid Map During Level Flight Experiment}
	\medskip
	\small
	The 2D projected map is easily produced in real-time. Candidate future poses, shown by arrows, have more blue color for larger objective functions, found with expected information gains and travel distances. Collision-free waypoints (blue line) serve as input to a constrained polynomial least-squares path (light green curve) for the robot controller to follow, where the desired pose (large axes) is tracked by the onboard controller from the current robot pose (small axes).
	\label{fig:exp2DMap}
\end{figure}

>>>>

The experiment involves a Pioneer ground vehicle producing a probabilistic occupancy grid map in real time. The robot motion is governed by the information gain-maximizing policy described in Chapter \ref{chap:ae2D}.

\subsection{Hardware Configuration}
The Pioneer 3 ground robot (Figure \ref{fig:Pioneer}) is chosen for this experiment because of its reliability and simple operation. The vehicle accepts two inputs, namely linear velocity (aligned with the robot wheels) and angular velocity (about a central axis passing vertically through the robot). The robot pose is estimated via Vicon Tracker, which provides the location and attitude of a rigid body. The depth readings are obtained by a Kinect depth sensor. Since the experiment is to map and explore a 2D environment, only a single central row of the 3D Kinect depth scan provide the necessary measurements. The robot captures an experimental environment with walls constructed from Styrofoam.

\begin{figure}
	\centering{
    	\begin{subfigure}[b]{0.3\textwidth}
	\centering
        		\includegraphics[height=0.7\textwidth]{pioneer.png}
        		\caption{Pioneer 3 Vehicle}
        		\label{fig:PioneerStockImage}
    	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
	\centering
        		\includegraphics[height=0.7\textwidth]{pioneer_side.png}
        		\caption{Side View}
        		\label{fig:PioneerSide}
    	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
	\centering
        		\includegraphics[height=0.7\textwidth]{pioneer_kinect.png}
        		\caption{Front View with Kinect}
        		\label{fig:PioneerSide}
    	\end{subfigure}
	}
\caption{Pioneer Robot}
	\medskip
	\small
	The Pioneer 3 robot serves as a reliable experimental platform for 2D mapping and autonomous exploration using a Microsoft Kinect.
\label{fig:Pioneer}
\end{figure}

@@

The software structure is similar to ROS nodes Section \ref{sec:Ae2DNumExamples}, which simply involves a mapping node, an exploration node, and a visualization node using OpenGL libraries~\cite{openGL}. The only differences are eliminating the simulator (Stage) and adding synchronization among the sensors, which is of high importance to the proposed occupancy grid mapping approach. Any time delay between the robot pose estimation and the sensor depth readings can cause conflicting information, which may be harmful to the probabilistic map. Thus, ROS approximate message filters are applied such that the pose from Vicon Tracker ($100$Hz) and the Microsoft Kinect ($30$Hz) are nearly synchronized, which provides validity of the assumption that the measurement ray positions and directions are known deterministically.

\subsection{Exploring and Mapping a 2D Environment}
The environment consists of Styrofoam walls on a flat floor. The perimeter is rectangular, with several obstacles and angled walls (see Figure \ref{fig:ExpSetupPhoto}). The robot autonomously explored the space using the complete Cartesian searching approach, and Dijkstra's algorithm provides collision-free waypoints to the optimal future poses. Based on these waypoints, a constrained least squares polynomial fitting generates a smooth trajectory to follow the waypoints with fixed velocity. Finally, a simple controller is implemented such that the Pioneer follows the trajectory by moving and orienting toward the desired robot location $1$ sec in the future.

@@

The quadrotor takes off, completes a rotation to understand its immediate surroundings, then explores the space over $2$ minutes and $47$ seconds, shown in Figure \ref{fig:expFilming}. Figure \ref{fig:exp3DMap} shows the probabilistic 3D map generated in real-time at four selected times, and the corresponding 2D projected maps (x-direction upward) are illustrated in Figure \ref{fig:exp2DMap}, where arrows represent pose candidates and a trajectory is shown to the optimal pose. Figure \ref{fig:expH} shows the total map entropy decreasing over the experiment duration. A video of the experiment can be found at \href{https://www.youtube.com/watch?v=I_1rXV2XRqk}{\WriteBlue{https://www.youtube.com/watch?v=I\_1rXV2XRqk}}.

\begin{figure}[!t]
\centering{
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 20cm 4cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_0sec.jpg}
        		\caption{$0$ sec}
    	\end{subfigure}
	\hspace*{0.04\columnwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 20cm 4cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_20sec.jpg}
        		\caption{$20$ sec}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 20cm 4cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_40sec.jpg}
        		\caption{$40$ sec}
    	\end{subfigure}
	\hspace*{0.04\columnwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 20cm 4cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_60sec.jpg}
        		\caption{$60$ sec}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 20cm 4cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_80sec.jpg}
        		\caption{$80$ sec}
    	\end{subfigure}
	\hspace*{0.04\columnwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 20cm 4cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_100sec.jpg}
        		\caption{$100$ sec}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 20cm 4cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_120sec.jpg}
        		\caption{$120$ sec}
    	\end{subfigure}
	\hspace*{0.04\columnwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 20cm 4cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_140sec.jpg}
        		\caption{$140$ sec}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 20cm 4cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_160sec.jpg}
        		\caption{$160$ sec}
    	\end{subfigure}
	\hspace*{0.04\columnwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 20cm 4cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_167sec.jpg}
        		\caption{$167$ sec (end)}
    	\end{subfigure}
}
	\caption{Level Flight Experiment}
	\medskip
	\small
	During the first minute, the robot slowly takes off and does an initial rotation, then explores the space in the remaining time.
	\label{fig:expFilming}
\end{figure}

\begin{figure}[!t]
\centering{
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 1cm 4cm 19cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_0sec.jpg}
        		\caption{$0$ sec}
    	\end{subfigure}
	\hspace*{0.04\columnwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 1cm 4cm 19cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_20sec.jpg}
        		\caption{$20$ sec}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 1cm 4cm 19cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_40sec.jpg}
        		\caption{$40$ sec}
    	\end{subfigure}
	\hspace*{0.04\columnwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 1cm 4cm 19cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_60sec.jpg}
        		\caption{$60$ sec}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 1cm 4cm 19cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_80sec.jpg}
        		\caption{$80$ sec}
    	\end{subfigure}
	\hspace*{0.04\columnwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 1cm 4cm 19cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_100sec.jpg}
        		\caption{$100$ sec}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 1cm 4cm 19cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_120sec.jpg}
        		\caption{$120$ sec}
    	\end{subfigure}
	\hspace*{0.04\columnwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 1cm 4cm 19cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_140sec.jpg}
        		\caption{$140$ sec}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 1cm 4cm 19cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_160sec.jpg}
        		\caption{$160$ sec}
    	\end{subfigure}
	\hspace*{0.04\columnwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[trim={25cm 1cm 4cm 19cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_167sec.jpg}
        		\caption{$167$ sec (end)}
    	\end{subfigure}
}
	\caption{3D Occupancy Grid Map During Level Flight Experiment}
	\medskip
	\small
	The 3D occupancy grid map is overlaid with point cloud measurements. The map probabilities directly rely on the Xtion and Hokuyo measurements and the sensor stochastic properties.
	\label{fig:exp3DMap}
\end{figure}

@@

%\begin{figure}[!t]
%\centering{
%    	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[trim={5cm 0cm 6cm 0cm}, clip, width=\textwidth]{experiment_ogm3D_0min.jpg}
%        		\caption{$0$ min}
%    	\end{subfigure}
%	\hspace*{0.04\columnwidth}
%    	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[trim={5cm 0cm 6cm 0cm}, clip, width=\textwidth]{experiment_ogm3D_1min.jpg}
%        		\caption{$1$ min}
%    	\end{subfigure}
%}
%\centering{
%    	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[trim={5cm 0cm 6cm 0cm}, clip, width=\textwidth]{experiment_ogm3D_2min.jpg}
%        		\caption{$2$ min}
%    	\end{subfigure}
%	\hspace*{0.04\columnwidth}
%    	\begin{subfigure}[t]{0.4\columnwidth}
%           	\centering
%          	\includegraphics[trim={5cm 0cm 6cm 0cm}, clip, width=\textwidth]{experiment_ogm3D_2min47sec.jpg}
%        		\caption{$2$ min $47$ sec (end)}
%    	\end{subfigure}
%}
%	\caption{3D Occupancy Grid Map During Level Flight Experiment}
%	\medskip
%	\small
%	The 3D occupancy grid map is overlaid with point cloud measurements. The map probabilities directly rely on the Xtion and Hokuyo measurements and the sensor stochastic properties.
%	\label{fig:exp3DMap}
%\end{figure}

\begin{figure}[!t]
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={0cm 19.8cm 45.5cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_0sec.jpg}
        		\caption{$0$ sec}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={0cm 19.8cm 45.5cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_20sec.jpg}
        		\caption{$20$ sec}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={0cm 19.8cm 45.5cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_40sec.jpg}
        		\caption{$40$ sec}
    	\end{subfigure}
}
\\
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={0cm 19.8cm 45.5cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_60sec.jpg}
        		\caption{$60$ sec}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={0cm 19.8cm 45.5cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_80sec.jpg}
        		\caption{$80$ sec}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={0cm 19.8cm 45.5cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_100sec.jpg}
        		\caption{$100$ sec}
    	\end{subfigure}
}
\\
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={0cm 19.8cm 45.5cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_120sec.jpg}
        		\caption{$120$ sec}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={0cm 19.8cm 45.5cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_140sec.jpg}
        		\caption{$140$ sec}
    	\end{subfigure}
	\hspace*{0.02\columnwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={0cm 19.8cm 45.5cm 0cm}, clip, width=\textwidth]{NRL_quadrotor_4panes_160sec.jpg}
        		\caption{$160$ sec}
    	\end{subfigure}
}
\\
\centering{
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_2min47sec_2D_labeled.jpeg}
        		\caption{$167$ sec (end)}
    	\end{subfigure}
}
	\caption{2D Projected Occupancy Grid Map During Level Flight Experiment}
	\medskip
	\small
	The 2D projected map is easily produced in real-time. Candidate future poses, shown by arrows, have more blue color for larger objective functions, found with expected information gains and travel distances. Collision-free waypoints (blue line) serve as input to a constrained polynomial least-squares path (light green curve) for the robot controller to follow, where the desired pose (large axes) is tracked by the onboard controller from the current robot pose (small axes).
	\label{fig:exp2DMap}
\end{figure}
